Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2021-02-18 09.0_manuscript.rmd
changed to groundhog

```{r, include=FALSE, echo = FALSE}
if(!require("pacman", quietly=TRUE)) install.packages("pacman")
suppressPackageStartupMessages(
  pacman::p_load(bookdown, knitr, pander, citr, broom))
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

@@

\
We removed those species that would be leafless in March 1997 because $\mathrm{\delta}$^2^H~xylem~ for these species may not be linked with water sourced at the time of measurement and thus not comparable to species that had leaves. We also removed one species whose $\mathrm{\delta}$^2^H~xylem~ was in the uncertain depth range. For each model of ERD (Eq. \@ref(eq:M-chosen) and alternatives in SI), modeled species ERD was regressed against species $\mathrm{\delta}$^2^H~xylem~ for a maximum of six species.

>>>>

```{r, include=FALSE, echo = FALSE}
if (!require("groundhog", quietly=TRUE)) install.packages("groundhog"); library(groundhog)
groundhog.day = "2020-04-01"
pkgs=c('knitr', 'pander', 'citr', 'broom')
suppressPackageStartupMessages(groundhog.library(pkgs, groundhog.day))
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

@@

\We removed one species with a $\mathrm{\delta}$^2^H value of -33.5 (SE$\pm$2.6) which is particularly difficult to assign a source-water depth given the uncertainty in soil water $\mathrm{\delta}$^2^H data by depth (see Fig S3). $\mathrm{\delta}$^2^H~xylem~ from leafless trees may not be linked with water sourced at the time of measurement and thus may not be comparable to species that had leaves. Leaflessness status of sampled trees is not recorded in [@Meinzer:2001]. We therefore removed five species that are typically leafless in March (Joseph Wright, personal observation), that is, the month of $\mathrm{\delta}$^2^H~xylem~ sampling. For each model of ERD (Eq. \@ref(eq:M-chosen) and alternatives in SI), modeled species ERD was regressed against species $\mathrm{\delta}$^2^H~xylem~ for a maximum of six species.
